Approximation as Differentiation

### 2025-05-05 appendix/notes/auto-diff.tex
Ok think I get how to see Diff as subcategory of Fam(FinVect).

\noindent and again we can define a corresponding category $\Diff^*$ of such maps where composition respects
the (backward) chain rule.

@@

>>>>

\noindent and again we can define a corresponding category $\Diff^*$ of such maps where composition of the
cotangent maps respects the (backward) chain rule.

@@

We can think of $\Diff$ as the subcategory of $\Fam(\FinVect)$ where the objects are just finite vector spaces
$\RR^n$. There is no need to pair with an $\RR^n$-indexed family of finite vector spaces, since the tangent
space for any $x \in \RR^n$ is simply $\RR^n$. Similarly the morphisms are fully specified by the pair of a
smooth function $f: \RR^m \to \RR^n$ and constant family of linear maps $\{\delta f_x: \RR^m \linearto
\RR^n\}_{x \in \RR^m}$.
